Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-24 article/article.Rmd
Commit 2024-05-23 20:08
Commit 2024-05-24 11:10

-  max value ECE
  relative to other works max values

Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies} we have
computed the distribution of the number of occurrences of ECE events by month in
Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. Here the most active
period is in the spring and the start of the summer (March -- June), followed by the
late fall (Septemcer and October).

.......

@@

```{r echo=FALSE, fig.cap="Distribution of ECE above 'clear sky' reference"}
knitr::include_graphics("../images/extremedistributions-2.png")
```

@@

-   SZA

@@

Created a clear sky approximation and a long term change representation for a period of 30 years.

Identify CE events and found a trend on .....
The climatology of CE occurrences over the whole period and
the magnitude of the CE events.
We estabished the occurances of extreme CE events ...

>>>>

<!-- -  max value ECE -->
<!--   relative to other works max values -->

Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies} we have
computed the distribution of the number of occurrences of ECE events by month in
Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. The most active period
for ECE events is in the spring and the start of the summer (March -- June), followed
by a period in the late fall (September and October).  This is probably an effect of
the weather characteristics of those periods where, there are continuous alternations
between clear sky periods and clouds.

@@

```{r echo=FALSE, fig.cap="Distribution of ECE above clear sky threshold."}
knitr::include_graphics("../images/P-extreme-distribution-1.png")
```

@@

<!-- -   SZA -->

@@

By creating a clear sky approximation of the GHI, which can represent the long- and
short-term variation of the expected clear sky GHI, we were able to identify cases of 
CE events.
By analysing the CE cases we found

The climatology of CE occurrences over the whole period and

the magnitude of the CE events.
We estabished the occurances of extreme CE events ...
The characteristic of the duration of "continuous" CE events.
with their magnitude occurnacies and climatology

Our find have similarities with other mediterranean / europe sites.

The interaction of GHI with the clouds through this period shows a systematic change.
